\textbf{\huge EHDA closed loop control system based on real time non-visual spray mode classification}\\ (Center, Bold, Times New Roman 14, maximum 15 words in english)

### 2023-01-20 Documentation/WT group/article1/main.tex
documentation

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance and efficiency. EHDA is a method of atomizing liquids using an electric field, which can generate droplets smaller than the nozzle diameter with a controlled droplet size. The system uses current data to classify the spray mode dynamics in real-time and adjust EHDA parameters such as pump flowrate and power supply voltage to reach the desired spray mode and stabilize it. The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous methods. The potential applications of the system are discussed, including in industrial processes such as spray coating and inkjet printing. EHDA has been widely used in various fields such as agriculture, biomedical and energy, specifically in the production of micron- and nano-size droplets for better control and efficient in the process.

@@

		}
		\textbf{\textit{Keywords}}: \textit{Keyword 1; keyword 2; keyword 3; keyword 4; keyword 5}
	\end{abstract}
\noindent\rule{15cm}{0.4pt}

\section{Introduction (10pt, bold)}
The introduction is about 400-600 words and provides background information, previous references related to the main topic, reason, purpose of the research, and the novelty of the research.  Content should be relatively non-technical, but clear enough for a knowledgeable reader to understand the manuscript’s contribution. Explain what the purpose of the research is and why the research was conducted the main body of the article should begin with an introduction, which provides further details on the purpose of the paper, motivation, research methods, and findings. For citations use numbering which must be used for reference titles, for example, citations for journals consisting of 1 article  \cite{Septiawan1} or two articles \cite{Septiawan2}, \cite{Lucy}, while for writing citations of more than two articles \cite{Gingold} - \cite{Morikawa}.

>>>>

\noindent\rule{15cm}{0.5pt}
	\begin{abstract}
		This article presents a closed-loop control system for EHDA (Electrohydrodynamic Atomization) that utilizes real-time, non-visual spray mode classification to improve performance, accuracy and efficiency in both research and industries applications.
		EHDA is a method of atomizing liquids using an electric field, which can generate droplets smaller than the nozzle diameter with a controlled droplet size.
		The system uses current data to classify the spray mode dynamics in real-time and adjust EHDA parameters such as pump flowrate and power supply voltage to reach the desired spray mode and stabilize it.
		The proposed control algorithm is able to achieve improved accuracy and reduced waste compared to previous manual methods.
		The potential applications of the system are discussed, including in industrial processes such as spray coating and gas odorizing.

@@

		}
		\textbf{\textit{Keywords}}: \textit{Electrospray; EHDA Control System; EHDA Automation; keyword 4; keyword 5}
	\end{abstract}
\noindent\rule{15cm}{0.4pt}

\section{Introduction (10pt, bold)  --> Do Luewtons Timeline}
The introduction is about 400-600 words and provides background information, previous references related to the main topic, reason, purpose of the research, and the novelty of the research.  Content should be relatively non-technical, but clear enough for a knowledgeable reader to understand the manuscript’s contribution. Explain what the purpose of the research is and why the research was conducted the main body of the article should begin with an introduction, which provides further details on the purpose of the paper, motivation, research methods, and findings. For citations use numbering which must be used for reference titles, for example, citations for journals consisting of 1 article  \cite{Septiawan1} or two articles \cite{Septiawan2}, \cite{Lucy}, while for writing citations of more than two articles \cite{Gingold} - \cite{Morikawa}.
